---
title: "Question 22"
author: |
  | Mohit Sharma: [LinkedIn](https://www.linkedin.com/in/mohit-sharma-82030487/), [Twitter](https://twitter.com/mohitsh48631107)
  | [GitHub Site](https://mohit2152sharma.github.io/Data-Science-Question-A-Day/), [Repository](https://github.com/mohit2152sharma/Data-Science-Question-A-Day)
date: "13 November 2019"
output: 
  html_document:
    theme: united
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning=FALSE,message=FALSE)
```

#### Question

The difference between $lm(y$ ~ $x*z)$ and $lm(y$ ~ $I(x*z))$, assuming x and z be numeric values is:

  1. eq 1 has interaction term 
  2. eq 2 has interaction term
  3. Both are same, diff by chance
  4. I don't know
  
#### Answer
Equation 1 has interaction term whereas equation 2 doesn't. $x*z$ indicates the cross of x and z which is equivalent to $x + z + x:z$ where $x:z$ indicates the set of terms obtained by taking the interactions of all terms in fist with all terms in second *(Source: lm documentation)*. 
Equation 2 doesn't have interaction term. $I(x*z)$ is equivalent to the product of x and z.
In function formula, I is used to inhibit the interpretation of operators as formula operators, so they are used as arithmetical operators only.

*An Example*
```{r}
library(MASS)

model1 = lm(medv~lstat*age, data=Boston)
model2 = lm(medv~I(lstat*age), data=Boston)
```

Model 1 coefficients
```{r}
summary(model1)$coefficients
```

Model 2 coefficients
```{r}
summary(model2)$coefficients
```

As we can see from the above example, the models are giving different coefficients because of the difference in formula.

If you like the question, how about some love and coffee: <a href='https://www.buymeacoffee.com/NgFs2zX'>Buy me a coffee</a>