---
title: "Question 28"
author: |
  | Mohit Sharma: [LinkedIn](https://www.linkedin.com/in/mohit-sharma-82030487/), [Twitter](https://twitter.com/mohitsh48631107)
  | [GitHub Site](https://mohit2152sharma.github.io/Data-Science-Question-A-Day/), [Repository](https://github.com/mohit2152sharma/Data-Science-Question-A-Day)
date: "20 November 2019"
output: 
  html_document:
    theme: united
    highlight: tango
---

#### Question

`which()` operator in R is a handy func when it comes to subsetting. It converts boolean representation to integer representation. Should I expect same result from following expression?

```{r}
x = c(1,0,0,0,1,1,0)
y = x < 0

which(y)
y
```

#### Answer

No, as `which()` coverts boolean representation to integer representation and returns the indices which are TRUE for a logical object.
So if I run the above example, I get the following output:
```{r}
x = c(1,0,0,0,1,1,0)
y = x < 0

which(y)
y
```
`which(y)` returns a zero vector whereas `y` returns a vector of same length as x with all indices being FALSE, which is expected as y is always FALSE.
What's happening behind the scene with `which()` is, `which(y)` tries to find the indices where the logical operation is TRUE but since it's always false `which(y)` doesn't return anyting.

This information is often useful when subsetting a dataframe (or a list etc) where you wish to exclude certain values using a logical operation but you are not sure if that logical operation has a possibility of being FALSE at all instances because `x[!which(y)]` would yield different results compared to `x[!y]`.

Thanks for reading. If you like the question, how about some love and coffee: <a href='https://www.buymeacoffee.com/NgFs2zX'>Buy me a coffee</a>