---
title: "Question 23"
author: |
  | Mohit Sharma: [LinkedIn](https://www.linkedin.com/in/mohit-sharma-82030487/), [Twitter](https://twitter.com/mohitsh48631107)
  | [GitHub Site](https://mohit2152sharma.github.io/Data-Science-Question-A-Day/), [Repository](https://github.com/mohit2152sharma/Data-Science-Question-A-Day)
date: "14 November 2019"
output: 
  html_document:
    theme: united
    highlight: tango

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning=FALSE,message=FALSE)
```

#### Question

Out of 10k obs in my sample, I have 1k obs belonging to category 1 and 9k obs to category 0. I build a binary classifier model that always predicts category 0 and got 90% accuracy on my training set. Is this a good model?

#### Answer

No the model is not good. There are two types of error being made here.

  > One, the model incorrectly assigns the variable of category 1 to category 0 and the second being, model incorrectly assigns the variable of category 0 to category 1.

It's often of interest to see which error is being made. Take for example if you are building a spam mail detection system. Your sample includes lots of examples of spam mails whereas very few examples of not-spam mail, let's say 9k spam mail examples and 1k not-spam mail example. If you happen to build a basic classifier model which always predict spam, even though the model is accurate 90% of time, it is not useful because this model would classify all the useful not-spam mail to spam mail.

A confusion matrix is a simple and useful way to display this information.

```{r confusion matrix}
actual = factor(c(1, 1, 0, 1, 0, 0, 1, 0, 0, 0), labels=c('Spam', 'Not Spam'))
predicted = factor(c(1, 0, 0, 1, 0, 0, 1, 1, 1, 0), labels=c('Spam', 'Not Spam'))

cm = caret::confusionMatrix(predicted, actual)
cm$table
```

In the above sample example, the columns indicate our true values whereas rows indicate our predicted values. So the way to read this table would be: Out of 6 Spam emails, our model predicted 4 emails as spam and 2 as Not spam. Similary, Out of 4 Not spam emails, our model predicted 1 email as spam email whereas 3 as not spam mails.

If you like the question, how about some love and coffee: <a href='https://www.buymeacoffee.com/NgFs2zX'>Buy me a coffee</a>
