---
title: "Question 25"
author: |
  | Mohit Sharma: [LinkedIn](https://www.linkedin.com/in/mohit-sharma-82030487/), [Twitter](https://twitter.com/mohitsh48631107)
  | [GitHub Site](https://mohit2152sharma.github.io/Data-Science-Question-A-Day/), [Repository](https://github.com/mohit2152sharma/Data-Science-Question-A-Day)
date: "16 November 2019"
output: 
  html_document:
    theme: united
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Question

Given a linear model, `mod <- lm(mpg ~ wt, data = mtcars)`, how would you extract the estimate of `wt`?

  1. `summary(mod)$coefficients['wt', 'Estimate']`
  2. `summary(mod)$coefficients[2,1]`
  3. Both are correct

#### Answer
Let's first create the model and look at how the summary of `mod` looks like.
```{r}
mod = lm(mpg ~ wt, data = mtcars)
results = summary(mod)
results
```
Using `str()` I can see the structure of results and also its type.
```{r}
str(results)
```
As I can see, `results` is a list (or in other words, `summary()` returns a list). You can also use `typeof()` and `names()` to check results's type and what all it contains.
```{r}
typeof(results)
```
```{r}
names(results)
```
So `results` is a list and know that coefficients of `wt` is stored in `coefficients`. Now it's just become the question of indexing a list and there are multiple ways to do it.
```{r}
coeff_wt = results[['coefficients']]
coeff_wt
```
```{r}
coeff_wt = results$coefficients
coeff_wt
```
Now, need to extract estimate of `wt`, will start by checking the object class of coeff_wt.
```{r}
class(coeff_wt)
```
Ahh, it's a matrix and there are multiple ways to index matrix.
  1. Using integer indexing:
```{r}
estimate = coeff_wt[2,1]
estimate
```
  2. Using row names and column names
```{r}
estimate = coeff_wt['wt', 'Estimate']
estimate
```

Summarizing the whole operation in single command
```{r}
mod = lm(mpg ~ wt, data = mtcars)
summary(mod)$coefficients['wt', 'Estimate']
```

Thanks for reading. If you like the question, how about some love and coffee: <a href='https://www.buymeacoffee.com/NgFs2zX'>Buy me a coffee</a>