---
title: "Question 25"
author: |
  | Mohit Sharma: [LinkedIn](https://www.linkedin.com/in/mohit-sharma-82030487/), [Twitter](https://twitter.com/mohitsh48631107)
  | [GitHub Site](https://mohit2152sharma.github.io/Data-Science-Question-A-Day/), [Repository](https://github.com/mohit2152sharma/Data-Science-Question-A-Day)
date: "16 November 2019"
output: 
  html_document:
    theme: united
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Question

Given a linear model, `mod <- lm(mpg ~ wt, data = mtcars)`, how would you extract the estimate of `wt`?

Source: <a href='https://adv-r.hadley.nz/vectors-chap.html'>Advanced R by Hadley Wickham</a>

  1. `summary(mod)$coefficients['wt', 'Estimate']`
  2. `summary(mod)$coefficients[2,1]`
  3. Both are correct

#### Answer
If in case, confusion arises about how to extract variables from a model (not just linear). Try this approach:

  1. see what all the model is returning and where the respective parameter is stored, using str()
  2. see the type of element where the respective parameter is stored like list, dataframe, matrix etc.
  3. Once you know that, it just becomes a question of accessing elements from list, dataframe etc.
  
Let's first create the model and look at how the summary of `mod` looks like.
```{r}
mod = lm(mpg ~ wt, data = mtcars)
results = summary(mod)
results
```
Using `str()` I can see the structure of results and also its type.
```{r}
str(results)
```
As I can see, `results` is a list (or in other words, `summary()` returns a list). You can also use `typeof()` and `names()` to check results's type and what all it contains.
```{r}
typeof(results)
```
```{r}
names(results)
```
So `results` is a list and know that coefficients of `wt` is stored in `coefficients`. Now it's just become the question of indexing a list and there are multiple ways to do it.
```{r}
coeff_wt = results[['coefficients']]
coeff_wt
```
```{r}
coeff_wt = results$coefficients
coeff_wt
```
Now, need to extract estimate of `wt`, will start by checking the object class of coeff_wt.
```{r}
class(coeff_wt)
```
It's a matrix and there are multiple ways to index matrix.
  1. Using integer indexing:
```{r}
estimate = coeff_wt[2,1]
estimate
```
  2. Using row names and column names
```{r}
estimate = coeff_wt['wt', 'Estimate']
estimate
```

Summarizing the whole operation in single command
```{r}
mod = lm(mpg ~ wt, data = mtcars)
summary(mod)$coefficients['wt', 'Estimate']
```

#### Edit
As it happens, there is a better way to index. Thanks to people on twitter. You can skip, using `summary()`. `mod` is a list, to index list I can use `$`, `coefficients` has named attribute `wt`, which you can use to get wt coefficient.
```{r}
mod = lm(mpg ~ wt, data = mtcars)
mod$coefficients[['wt']]
```
``` {r}
#from tidyverse
coef(mod)[['wt']]
```

Thanks for reading. If you like the question, how about some love and coffee: <a href='https://www.buymeacoffee.com/NgFs2zX'>Buy me a coffee</a>