---
title: "Environments in R"
author: |
  | Mohit Sharma: [LinkedIn](https://www.linkedin.com/in/mohit-sharma-82030487/), [Twitter](https://twitter.com/mohitsh48631107)
  | [GitHub Site](https://mohit2152sharma.github.io/Data-Science-Question-A-Day/), [Repository](https://github.com/mohit2152sharma/Data-Science-Question-A-Day)
date: "28 November 2019"
output: 
  html_document:
    theme: united
    highlight: tango
---

### Question

Environments in R behave similar to list. Would the following code snippet work?

```{r, results=FALSE, eval=FALSE}
#using pkg rlang to create environment

env = rlang::env(
  'a' = 1,
  'b' = 1:10,
  'c' = list(1,'x', 2)
)

env[[1]]

```


### Answer

Calling the objects of environment using index will not work as the names (of objects) in 
environment are unordered. It will throw a subsetting error.

```{r, error=TRUE}
env = rlang::env(
  'a' = 1,
  'b' = 1:10,
  'c' = list(1,'x', 2)
)

env[[1]]
```

Use names to call out objects. For example:
```{r}
env = rlang::env(
  'a' = 1,
  'b' = 1:10,
  'c' = list(1,'x', 2)
)

env[['a']] #or env$a
```

Reference: <a href='https://advanced-r-solutions.rbind.io/environments.html'>Advanced R by Hadley Wickham</a>

Thanks for reading. If you like the question, how about some love and coffee: <a href='https://www.buymeacoffee.com/NgFs2zX'>Buy me a coffee</a>