---
title: 'Question 31: Super assignment operator'
author: |
  | Mohit Sharma: [LinkedIn](https://www.linkedin.com/in/mohit-sharma-82030487/), [Twitter](https://twitter.com/mohitsh48631107)
  | [GitHub Site](https://mohit2152sharma.github.io/Data-Science-Question-A-Day/), [Repository](https://github.com/mohit2152sharma/Data-Science-Question-A-Day)
date: "23 November 2019"
output: 
  html_document:
    theme: united
    highlight: tango
---

### Question

Super assignment operator `<<-` can be used for assignment in parent environment. Which of the following is TRUE for the following code?

  1. A = B = C
  2. C > B > A
  3. C < B < A

```{r, results=FALSE}

x <- 0

f <- function(){
  x <<- x + 1
  x
}

#1st execution
A = f()
#2nd execution
B = f()
#3rd execution
C = f()
```


### Answer

`<<-` is known as super assignment operator. In contrast to the regular assignment operator `<-` which does the assignment in current environment, `<<-` does the assignment in parent environment. If in case it doesn't find the variable, it will create the variable in global environment. See for example below:

I have defined a function `f` with a variable `y` in it to which I have assigned 1. If I try to access `y` outside function, I get the error, as `y` doesn't exist in global environment. It only exists in `f`'s environment.
```{r, error=TRUE}
f <- function(){
  y <- 1
}
#function call
f()
y
```
But if I rewrite the above code using `<<-`, I don't get any error. `y` is now defined in global environment.
```{r}
f <- function(){
  y <<- 1
}
#function call
f()
y
```

So for the above question, option $2.$ $C>B>A$ is correct.
```{r}
x <- 0

f <- function(){
  x <<- x + 1
  x
}

#1st execution
A = f()
#2nd execution
B = f()
#3rd execution
C = f()
```

As `C=3`, `B=2`, `A=1`. At the first execution, `f` returns `1` and also updates `x` in global environment to `1`. Similarly for the subsequent executions, `x` gets updated globally with an increment 1.
```{r}
A
B
C
```

In contrast, if I use `<-`, I would get `A=B=C=1`.
```{r}
x <- 0

f <- function(){
  x <- x + 1
  x
}

#1st execution
A = f()
#2nd execution
B = f()
#3rd execution
C = f()
```

```{r}
A
B
C
```


References:<a href='https://adv-r.hadley.nz/control-flow.html'> Advanced R by Hadley Wickham</a>

Thanks for reading. If you like the question, how about some love and coffee: <a href='https://www.buymeacoffee.com/NgFs2zX'>Buy me a coffee</a>
