---
title: 'Scoping in R'
author: |
  | Mohit Sharma: [LinkedIn](https://www.linkedin.com/in/mohit-sharma-82030487/), [Twitter](https://twitter.com/mohitsh48631107)
  | [GitHub Site](https://mohit2152sharma.github.io/Data-Science-Question-A-Day/), [Repository](https://github.com/mohit2152sharma/Data-Science-Question-A-Day)
date: "24 November 2019"
output: 
  html_document:
    theme: united
    highlight: tango
---

### Question
Although unadvisable, but it's interesting how scoping works in R. R allows function and variable to have same name. What does the following code return?

Source: <a href='ahttps://adv-r.hadley.nz/functions.html'>Advanced R by Hadley Wickham</a>

  1. Error
  2. 110
  3. 10

```{r, results=FALSE}
g09 <- function(x) x + 100
g10 <- function() {
  g09 <- 10
  g09(g09)
}
g10()
```


### Answer

Correct answer is 110. 
```{r}
g09 <- function(x) x + 100
g10 <- function() {
  g09 <- 10
  g09(g09)
}
g10()
```
This could only work when the function and variable are defined in different environments. When the function with same name is called, it ignores the non-functional objects like variables. In the above example, when function `g09()` is called, it igonres the variable `g09` and looks for the function object with `g09` name. Since both are defined in different environments, variable `g09` is defined in function `g10`'s environment, whereas `g09()` is defined in global environment, I don't get an error when executing the above code.


Thanks for reading. If you like the question, how about some love and coffee: <a href='https://www.buymeacoffee.com/NgFs2zX'>Buy me a coffee</a>