---
title: "data.frame's drop argument in R" 
author: |
  | Mohit Sharma: [LinkedIn](https://www.linkedin.com/in/mohit-sharma-82030487/), [Twitter](https://twitter.com/mohitsh48631107)
  | [GitHub Site](https://mohit2152sharma.github.io/Data-Science-Question-A-Day/), [Repository](https://github.com/mohit2152sharma/Data-Science-Question-A-Day)
date: "07 December 2019"
output: 
  html_document:
    theme: united
    highlight: tango
    includes:
      in_header: "ga_script.html"
---

### Question
Is `x` a dataframe of column one or a numeric vector?
```{r, eval=FALSE}
x = mtcars[, 'mpg']
```

### Answer
`x` is a numeric vector.
```{r}
x = mtcars[,'mpg']
is.vector(x, mode='numeric')
```
To get dataframe after subsetting, use the argument `drop=FALSE`.
```{r}
x = mtcars[,'mpg', drop=FALSE]
class(x)
```
This behaviour can often be source of bugs when writing a code pipeline, as intuitively you would expect it to return a one column dataframe. To avoid flattening of subsets, remember to use `drop=FALSE`.

Other option could be to use `tibble`, which always return a tibble.
```{r}
mtcars = dplyr::as_tibble(mtcars)
x = mtcars[, 'mpg']
class(x)
```



Thanks for reading. If you like the question, how about a tip: <a href='https://www.paypal.me/mohit2013'>PayPal TipJar</a>