---
title: 'Question 29: if and ifelse in R'
author: |
  | Mohit Sharma: [LinkedIn](https://www.linkedin.com/in/mohit-sharma-82030487/), [Twitter](https://twitter.com/mohitsh48631107)
  | [GitHub Site](https://mohit2152sharma.github.io/Data-Science-Question-A-Day/), [Repository](https://github.com/mohit2152sharma/Data-Science-Question-A-Day)
date: "21 November 2019"
output: 
  html_document:
    theme: united
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Question

In base R, there are two quite similar ways to work with conditional statements. One is `if(condition) .... else ....` and the second is `ifelse(condition, TRUE Action, FALSE action)`.

The difference between the two is that the first one works with scalars whereas second one works with vector also?

### Answer

Yes, the difference between the two is that the first one works with scalars whereas second one works with vector also. When you use the first one i.e. `if(condition) ..... else .....` on a vector you will see a warning message. Let's say for example, you want to find out which numbers in a vector are divisible by 5:
```{r}
x = c(5,4,3,5,1,10,2)
if(x%%5==0) TRUE else FALSE
```
As you can see in the warning message, the condition is only evaluated based on the first element of vector which turned out to be TRUE. The `if` only works with single TRUE and FALSE, it dosen't recycle the condition to the same length as the input vector.

If you are working with vectors, `ifelse()` should be the choice. For example:
```{r}
x = c(5,4,3,5,1,10,2)
ifelse(x%%5==0, TRUE, FALSE)
```

References:<a href='https://adv-r.hadley.nz/control-flow.html'> Advanced R by Hadley Wickham</a>

Thanks for reading. If you like the question, how about some love and coffee: <a href='https://www.buymeacoffee.com/NgFs2zX'>Buy me a coffee</a>
