---
title: "Matrices in R"
author: |
  | Mohit Sharma: [LinkedIn](https://www.linkedin.com/in/mohit-sharma-82030487/), [Twitter](https://twitter.com/mohitsh48631107)
  | [GitHub Site](https://mohit2152sharma.github.io/Data-Science-Question-A-Day/), [Repository](https://github.com/mohit2152sharma/Data-Science-Question-A-Day)
date: "11 December 2019"
output: 
  html_document:
    theme: united
    highlight: tango
    includes:
        in_header: "../../analytics/ga_script.html"
---

### Question
Using the following command to create matrix in R, what would be the output?
```{r, eval=FALSE}
matrix(c(1:9), nrow=3, ncol=3)
```

  1. Option A
```{r, echo=FALSE, comment=NA}
matrix(c(1:9), nrow=3, ncol=3, byrow=TRUE)
```
  2. Option B
```{r,echo=FALSE,comment=NA}
matrix(c(1:9), nrow=3, ncol=3)
```

### Answer

The default behaviour of `matrix()` function is to fill the matrix by column. So option B is True, to fill the matrix by rows, one has the use `byrow` argument and set it to `TRUE`.
```{r, comment=NA}
matrix(c(1:9), nrow=3, ncol=3, byrow=TRUE)
```


Thanks for reading. If you find a correction, hit me up on <a href='https://twitter.com/data_question'>Twitter</a> and if you like the question, how about a tip: <a href='https://www.paypal.me/mohit2013'>PayPal TipJar</a>